Strings functions analysis

### 2022-08-30 article.tex
existing table filled

\usepackage{rotating}
\usepackage{debate}
\usepackage{tabularx}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

@@

@@

    \textbf{Rust (35)}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str.

    \begin{table*}
        \begin{tabular}{lllllllllll}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            \\ \hline

            String \textbf{capitalize} &  &  &  &  &  & &  &  & 1 & 1 \\

            Get \textbf{char-at} a given position &  &  &  &  &  & &  &  & 1 & 1 \\

            Strings \textbf{compare} &  &  &  &  &  & &  &  & n & n \\

            Strings \textbf{compare-ignore-case} &  &  &  &  &  & &  &  &  & \\

            Strings \textbf{concatenate} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{containts} substring &  &  &  &  &  & &  &  & n & n \\

            \textbf{count} of substring in string &  &  &  &  &  & &  &  &  & \\

            Check if \textbf{ends-with} a substring &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{equals} &  &  &  &  &  & &  &  & n & n \\

            \textbf{find-first} substring in string &  &  &  &  &  & &  &  & n & n \\

            \textbf{find-last} substring in string &  &  &  &  &  & &  &  & n & n \\

            \textbf{format} string by regexp &  &  &  &  &  & &  &  & n & n \\

            Get string \textbf{hash} &  &  &  &  &  & &  &  & n & n \\

            \textbf{insert} in string by index &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-alphabetic} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-empty} &  &  &  &  &  & &  &  & 1 & 1 \\

            Check if \textbf{is-hexadecimal} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-int} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-lowercase} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-uppercase} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{is-whitespace} &  &  &  &  &  & &  &  & n & n \\

            \textbf{join} list of strings &  &  &  &  &  & &  &  & n & n \\

            Get string \textbf{length} &  &  &  &  &  & &  &  & 1 & 1 \\

            Check if string \textbf{matches-regexp} &  &  &  &  &  & &  &  & n & n \\

            Get string \textbf{partition} &  &  &  &  &  & &  &  & n & n \\

            \textbf{repeat} string number of times &  &  &  &  &  & &  &  & n & n \\

            \textbf{replace-all} substrings by other &  &  &  &  &  & &  &  & n & n \\

            \textbf{replace-first} substrings by other &  &  &  &  &  &  &  &  &  & \\

            String \textbf{split} &  &  &  &  &  & &  &  & n & n \\

            Check if \textbf{starts-with} a substring &  &  &  &  &  & &  &  & n & n \\

            String \textbf{strip} &  &  &  &  &  & &  &  & n & n \\

            Get \textbf{substring} by positions &  &  &  &  &  & &  &  & n & 1 \\

            String \textbf{swap-case} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-float} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-int} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-lowercase} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{to-uppercase} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{trim-left} &  &  &  &  &  &  &  &  & n & n \\

            String \textbf{trim-righ} &  &  &  &  &  & &  &  & n & n \\

            String \textbf{reverse} &  &  &  &  &  & &  &  & n & 1 \\

            \textbf{remove} substring by positions &  &  &  &  &  & &  &  &  & \\

            String \textbf{uncapitalize} &  &  &  &  &  & &  &  &  & \\

            Get string \textbf{as-bytes} &  &  &  &  &  & &  &  &  & \\

            String \textbf{pop-back} &  &  &  &  &  & &  &  &  & \\

            Get string \textbf{as-chars} &  &  &  &  &  & &  &  &  & \\

            Get string \textbf{as-canonical} &  &  &  &  &  & &  &  &  & \\

            Check if \textbf{is-ascii}  &  &  &  &  &  & &  &  &  & \\

            String \textbf{copy} &  &  &  &  &  & &  &  &  & \\

            String \textbf{contains-any} &  &  &  &  &  & &  &  &  & \\

            String \textbf{reserve-capacity} &  &  &  &  &  & &  &  &  & \\

            String \textbf{shrink-to-fit} &  &  &  &  &  & &  &  &  & \\ \hline

        \end{tabular}
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{table*}

>>>>

\usepackage{amssymb}
\usepackage{rotating}
\usepackage{debate}
\usepackage{tabularx}
\usepackage{ffcode}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage[capitalize]{cleveref}
\usepackage{paralist}
\usepackage{cancel}
\usepackage{to-be-determined}
\usepackage{tikz}

@@

    \hl{todo add link to parsing repo}

@@

    \textbf{Rust (105)}: new, with\_capacity, from\_utf8, from\_utf8\_lossy, from\_utf16, from\_utf16\_lossy, from\_raw\_parts, from\_utf8\_unchecked, into\_bytes, as\_str, as\_mut\_str, push\_str, capacity, reserve, reserve\_exact, try\_reserve, try\_reserve\_exact, shrink\_to\_fit, shrink\_to, push, as\_bytes, truncate, pop, remove, retain, insert, insert\_str, as\_mut\_vec, len, is\_empty, split\_off, clear, drain, splice, into\_boxed\_str, as\_bytes, as\_bytes\_mut, as\_mut\_ptr, as\_ptr, bytes, ceil\_char\_boundary, char\_indices, chars, contains, encode\_utf16, ends\_with, eq\_ignore\_ascii\_case, escape\_debug, escape\_default, escape\_unicode, find, floor\_char\_boundary, get, get\_mut, get\_unchecked, get\_unchecked\_mut, is\_ascii, is\_char\_boundary, is\_empty, len, lines, lines\_any, make\_ascii\_lowercase, make\_ascii\_uppercase, match\_indices, matches, parse, repeat, replace, replacen, rfind, rmatch\_indices, rmatches, rsplit, rsplit\_once, rsplit\_terminator, rsplitn, slice\_mut\_unchecked, slice\_unchecked, split, split\_ascii\_whitespace, split\_at, split\_at\_mut, split\_inclusive, split\_once, split\_terminator, split\_whitespace, splitn, starts\_with, strip\_prefix, strip\_suffix, to\_ascii\_lowercase, to\_ascii\_uppercase, to\_lowercase, to\_uppercase, trim, trim\_end, trim\_end\_matches, trim\_left, trim\_left\_matches, trim\_matches, trim\_right, trim\_right\_matches, trim\_start, trim\_start\_matches.

    \begin{table*}
        \begin{tabular}{lllllllllll}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            \\ \hline
            String \textbf{capitalize} & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & \\
            Get \textbf{char-at} a given position & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ & & $\checkmark$ \\
            Strings \textbf{compare} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \\
            Strings \textbf{compare-ignore-case} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & $\checkmark$ & \\
            Strings \textbf{concatenate} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Check if \textbf{contains} substring & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            \textbf{count} of substring in string & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & & & $\checkmark$ & \\
            Check if \textbf{ends-with} a substring & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Check if \textbf{equals} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            \textbf{find-first} substring in string & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            \textbf{find-last} substring in string & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            \textbf{format} string by regexp & $\checkmark$ & $\checkmark$ & & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & \\
            Get string \textbf{hash} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
            \textbf{insert} in string by index & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
            Check if \textbf{is-alphabetic} & $\checkmark$ & $\checkmark$ & $\checkmark$ & & & & & & & \\
            Check if \textbf{is-empty} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & $\checkmark$ \\
            Check if \textbf{is-whitespace} & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & & \\
            \textbf{join} list of strings & & $\checkmark$ & & & & $\checkmark$ & $\checkmark$ & & $\checkmark$ & \\
            Get string \textbf{length} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Check if string \textbf{matches-regexp} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & & & \\
            Get string \textbf{partition} & & $\checkmark$ & & $\checkmark$ & & $\checkmark$ & & & & \\
            \textbf{repeat} string number of times & & & & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ \\
            \textbf{replace-all} substrings by other & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            \textbf{replace-first} substrings by other & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & & & $\checkmark$ \\
            String \textbf{split} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Check if \textbf{starts-with} a substring & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            String \textbf{strip} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            Get \textbf{substring} by positions & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            String \textbf{to-float} & & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & \\
            String \textbf{to-int} & & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & \\
            String \textbf{to-lowercase} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            String \textbf{to-uppercase} & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
            String \textbf{trim-left} & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ \\
            String \textbf{trim-right} & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & & $\checkmark$ & $\checkmark$ \\
            \textbf{remove} substring by positions & & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & $\checkmark$ \\
            Get string \textbf{as-bytes} & & $\checkmark$ & & $\checkmark$ & & & & & & $\checkmark$ \\
            String \textbf{pop-back} & & & $\checkmark$ & $\checkmark$ & & & & $\checkmark$ & & $\checkmark$ \\
            Get string \textbf{as-chars} & $\checkmark$ & & & $\checkmark$ & & & $\checkmark$ & & & $\checkmark$ \\
            Get string \textbf{as-canonical} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & & & \\
            Check if \textbf{is-ascii} & & $\checkmark$ & & $\checkmark$ & & & & & & $\checkmark$ \\
            String \textbf{copy} & $\checkmark$ & & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & & & \\
            String \textbf{reserve-capacity} & & & $\checkmark$ & & & & & $\checkmark$ & & $\checkmark$ \\
            String \textbf{reverse} & & $\checkmark$ & & $\checkmark$ & $\checkmark$ & & & $\checkmark$ & $\checkmark$ & \\
            \\ \hline
        \end{tabular}
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{table*}
